---
title: "Unit 1 - 3 Review Starter"
author: "Group 5"
date: "10.04.2021"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
sand_minerals <- read_csv("data/sand-minerals.csv")
location_descriptions <- read_csv("data/location-descriptions.csv")
density <- read_csv("data/density.csv")
solubility_hardness <- read_csv("data/solubility-hardness.csv")
```

## Exercises

### Exercise 1

```{r inspect-sand-minerals}
glimpse(sand_minerals) %>% 
  spec()
names(sand_minerals)
```

There are 23 rows and 2 variables in `sand_minerals`
Each row contains the minerals (Quart/Feldspar/Biotite) found in each location number (1 - 10).

### Exercise 2

```{r inspect-other-dataframes}
glimpse(location_descriptions)
glimpse(density)
glimpse(solubility_hardness)
names(location_descriptions)
names(density)
names(solubility_hardness)
```
- There are `r nrow(location_descriptions)` observations and `r ncol(location_descriptions)` variables in `location_descriptions`
- There are `r nrow(density)` observations and `r ncol(density)` variables in `density`
- There are `r nrow(solubility_hardness)` observations and `r ncol(solubility_hardness)` variables in `solubility_hardness`

For location_descriptions, each row represents both a location (double) and a description of that location (character).
For density, each row represents one mineral (chr) and its associated density value (dbl). 
For solubility_hardness, each row represents a mineral (chr), its associated solubility (chr), and hardness value (dbl).

### Exercise 3

```{r join-mineral-properties}
sand_mineral_density <- sand_minerals %>%
    left_join(density)%>%
  sand_mineral_density <-sand_minerals %>%
  left_join(solubility_hardness)
```
There are 23 rows in sand_mineral_density. It has the same amount of rows as sand_minerals

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.
